---
title: "Shiny in R"
author: "Yanan Wu"
date: "2024-10-01"
output: html_document
---
# Introduction

A Shiny app in R is a web application framework that allows users to create interactive and dynamic web apps directly from R without needing extensive web development skills. Shiny combines the power of R’s data analysis and visualization capabilities with an easy-to-use interface for building responsive, interactive applications.

Key important of every Shiny app: 
  1. UT (short for user interface) which defines how your app looks
  2. server function: defines how your app works 
  3. reactive programming:automatically update outputs when inputs change  

# Install and load Shiny package
```{r}
install.packages("shiny")
library('shiny)
```

# Create file
Create a file called *app.R* in your file directory. The *app.R* file is used to show how your app should look, and how it should behave. 

#Function of your app
1. Include a spatail data
2. Sidebar

[card with sidebar and without sidebar](https://shiny.posit.co/r/articles/build/layout-guide/)

# Load data and relevant packages 
```{r}
library(shiny);library(leaflet);library(sf);library(dplyr)

points_data <- st_read("cbsa_points.shp") 

tf_data = st_transform(points_data, crs = "+proj=longlat +datum=WGS84")
```

# Fluid page

https://mastering-shiny.org/action-layout.html

# Add title of your app
```{r}
titlePanel("Interactive Mortgage Map")
```

# Adding UI controls
Create a layout with a sidebar and main area. The sidebar contains UT controls. The main area contain outputs. 



# Running app
Click the *Run App* button in the document toolbar













